\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Prithvi Singh}}\\
	New Delhi $\cdot$ prithvi.chandla@gmail.com $\cdot$ 9810548792 $\cdot$ prithvisingh18.github.io\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Manav Rachna University}\hfill Faridabad, Haryana\\
B.Tech Computer Science \textit{Percentage: 74.60 \%} \hfill 2015 - 2019\\
\vspace{2mm}
\textbf{S.R.S Public School}\hfill Rohtak, Haryana\\
12th \textit{Percentage: 75.60 \%} \hfill 2014 - 2015\\
\vspace{2mm}
\textbf{D.A.V Public School}\hfill Rohtak, Haryana\\
10th \textit{Percentage: 77.9 \%} \hfill 2013 - 2014\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Foundation Futuristic Technologies} \hfill Faridabad\\
\textit{Python Developer} \hfill Oct 2017 | Nov 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked on the Python application which collected cell tower data surrounding an area.
	\item Fixed bugs and added functionality mostly UI.
	\item Reduced the starting time of the app.
	\item Used Python, Rasberry Pi, Kali Linux, PyQt, etc
\end{itemize}
\textbf{M19G} \hfill Remote\\
\textit{Software Development Intern} \hfill Dec 2017 | Jan 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Implemented a server which, took data from client and saved it on Cassandra Database Cluster.
	\item Used web-sockets for Real time communication between client and server as the client edited the code.
	\item Provided the client with the code, Client interprets the code with running instance of MicroPython compiled to Web Assembly .
	\item Worked on Progressive Web App using Polymer, editing Web Components according to need.
	\item Integrating the compiled MicroPython Interpreter in Web Assembly with the app.
	\item REST API to get the PWA from the server.
	\item Learned how to write scalable and readable Javascript code.
	\item Used Node.js, Express.js, Cassandra DB(NoSQL), Polymer CLI, GIT, MicroPython, Web Assembly, Emscripten etc.
\end{itemize}
\textbf{Naxap} \hfill Remote\\
\textit{Software Development Intern} \hfill May 2018 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked on Techyon, Web application that monitor for infringing ip addresses, domains, emails, contacts etc and performs vulnerability scans and validation using metasploit and w3af.
	\item Worked on there main page bytescare.com using hogen.js(compiler for Mustache templating language)
	\item Making REST API Endpoints for providing data for client. Using express.js
	\item Wrote tests testing various functionalities in Mocha.
	\item Used Node.js, Wappalyzer, Mocha, Metasploit(msfrpc), w3af(REST API), Nmap etc.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & JavaScript, Node.js, Angular.js, Python, C\#, Unity3D, Rust, Java, C, C++ \\
	Web Technologies:      & Rest API, Web Assembly, Progressive Web App                               \\
	Python Libraries:      & Scrapy, Selenium, numpy, scikit learn, PyQt etc.                          \\
	Operating System:      & Linux(Ubuntu, Kali, Fedora), Windows                                      \\
	Tools and software:    & Git, Weka, Sketch                                                         \\
\end{tabular}
\vspace{2mm}
\filbreak
\header{Projects}
{\textbf{Space War}} {\sl Unity3D} \\
An arcade space fighter game.\\
\vspace*{2mm}
{\textbf{Robot}} {\sl Arduino, C} \\
Robot controlled by mobile gyroscope.\\
\vspace*{2mm}
{\textbf{Database}} {\sl C, Make} \\
A database written in C.\\
\vspace*{2mm}
{\textbf{Amazon Review Scraper}} {\sl Python, lxml} \hfill https://github.com/prithvisingh18/Scrapers\\
Scrapes review for a particular product from amazon.\\
\vspace*{2mm}
{\textbf{Static Website Generator}} {\sl Python, html-parser} \hfill https://github.com/prithvisingh18/static-website-generator\\
Builds a static website using a template and data provided by the user.\\
\vspace*{2mm}
{\textbf{HTTP Server on Rust}} {\sl Rust} \hfill https://github.com/prithvisingh18/rust-server\\

\vspace*{2mm}
{\textbf{http-chat-server}} {\sl C} \hfill https://github.com/prithvisingh18/http-chat-server\\
chating on local network\\
\vspace*{2mm}
{\textbf{Block Breaker}} {\sl Unity3D, WebGL} \hfill https://prithvisingh18.github.io/BlockBreaker/\\
An arcade block based game.\\
\vspace*{2mm}
{\textbf{Racing Game}} {\sl Python, Pygame} \hfill https://github.com/prithvisingh18/hellogame\\
Racing Game using Pygame\\
\vspace*{2mm}
{\textbf{Open Source Contribution(PyBee VOC)}} {\sl Python, Java, Git.} \hfill https://github.com/pybee/voc/pull/739\\
Implement Python standard library function in Java for PyBee VOC(https://github.com/pybee/voc)\\
\vspace*{2mm}

\header{Publications}
\textbf{Big Data in Applications of Automated Systems} \hfill ICACCCN 2018\\

\vspace*{2mm}

\ 
\end{document}